On Secure Delegation of SampBQP with a Classical Client

### 2020-03-29 hamiltonian.tex
Relate V_Ham p_acc with fidelity to ground state

Now we state the main theorems that we'll work towards in this section.
The first one is the reduction from $\SampBQP$ to a local Hamiltonian instance, with some additional properties that will be convenient for us:
\begin{thm}
	\label{thm:LHReduction}
	Let $C$ be a circuit of size $T$. For any input string $x$, there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
		\item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
	\end{itemize}
\end{thm}

@@

\begin{algorithm}
	\caption{Check for ground state}
	\label{AlgGroundStateCheck}
		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
		Let $\ket\phi$ be the potential ground state to check.
		\begin{itemize}
			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\item Set $p_S = \frac{|d_S|}{D}$
			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
		\end{itemize}
\end{algorithm}

\begin{thm}
	Let $H$ have $O(\poly(T))$ nonzero components whose coefficients at most $O(\poly(T))$.
	Then \cref{AlgGroundStateCheck} accepts $\ket{\phi}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H_{C(x)}|\phi}$.
\end{thm}
\begin{prf}
	Here we follow \cite{PhysRevA.93.022326}.
	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
	\end{align*}
\end{prf}

>>>>

Now we state the main theorems that we'll work towards in this section.
The first one is the reduction from $\SampBQP$ to a local Hamiltonian instance, with some additional properties that will be convenient for us:
\begin{thm}
	\label{thm:LHReduction}
	Let $C$ be a circuit of size $T$. For any input string $x$, there exists a local Hamiltonian $H_{C(x)}$  with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms and $d_S\in O(T^4)$.
		\item $H_{C(x)}$ has $\ket{\psi_{C(x)}}$ as the unique ground state with eigenvalue $0$.
		\item For any state $\ket\phi$ such that $\braket{\phi|\psi_{C(x)}}=0$,  $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
		\item Its descriptions can be constructed by a $\BPP$ machine in polynomial time.
	\end{itemize}
\end{thm}

@@

\begin{algorithm}
	\caption{Check for ground state $\cVGS$}
	\label{AlgGroundStateCheck}
		Let $H=\sum_{S\in\mathcal{G}_{XZ}} d_S S$.
		Let $\ket\phi$ be the potential ground state to check.
		\begin{itemize}
			\item Set $D = \sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\item Set $p_S = \frac{|d_S|}{D}$
			\item Sample $\widetilde{S}$ from $\mathcal{G}_{XZ}$, weighted by $p_S$.
			\item Measure $\ket\phi$ in the $\widetilde{S}$ basis, recording the result as $\lambda_{\widetilde{S}}$.
			\item If $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$, accept. Otherwise, reject.
		\end{itemize}
\end{algorithm}

\begin{thm}
	\label{thm:HamCheck}
	Let $H$ have $O(T)$ nonzero terms whose coefficients are at most $O(T^4)$.
	\Ethan{Missing a bunch of other assumptions... Should just state $H$ as local Hamiltonian instance from earlier}
	Then $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
\end{thm}
\begin{prf}
	Here we follow \cite{PhysRevA.93.022326}.
	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\frac{O(1)}{T^5}\braket{\phi|H|\phi}
	\end{align*}
\end{prf}

\begin{cor}
	\Ethan{Consider merging this with theorem above}

	\label{cor:HamCheck}
	There exists some $c\in\bbR$ s.t.
	let $H_{C(x)}$ be as above and
	$\varepsilon\in\bbR$, then
	if $\cVGS$ accepts $\rho$ with probability at least $\frac{1}{2}-\frac{c\varepsilon}{T^5}$
	then $F(\rho, \psi_{C(x)})\geq1-\varepsilon$
\end{cor}
\begin{prf}
	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.

	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't.
	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\psi_{C(x)}, \phi)$.

	Now we have
	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\psi_{C(x)}, \phi))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
	which easily implies our claim for pure state inputs $\phi$.

	The argument generalizes easily to mixed state inputs $\rho$.
\end{prf}

### 2020-03-29 preliminaries.tex
Define fidelity
Relate V_Ham p_acc with fidelity to ground state

Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit. Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian matrices. We use $H\geq0$ to denote $H$ being positive semidefinite. Let $\lambda(H)$ be the smallest eigenvalue of $H$. The ground states of $H$ are the eigenvectors corresponding to $\lambda(H)$. For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$. For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.

@@

TODO Define fidelity

@@

\begin{thm}
	\label{thm:projection}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$. Then,
	$$\exists J=\frac{\poly(\norm{H_1})}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
\end{thm}

>>>>

Let $\mathcal{B}$ be the Hilbert space corresponding to one qubit. Let $H:\mathcal{B}^{\otimes N}\rightarrow\mathcal{B}^{\otimes N}$ be Hermitian matrices. We use $H\geq0$ to denote $H$ being positive semidefinite. Let $\lambda(H)$ be the smallest eigenvalue of $H$. The ground states of $H$ are the eigenvectors corresponding to $\lambda(H)$. For matrix $H$ and subspace $S$, let $H\big|_S=\Pi_S H \Pi_S$, where $\Pi_S$ is the projector onto the subspace $S$. For a $T$-qubit Hilbert space, let the state $\ket{\widehat{t}}=\ket{1}^{\otimes t}\otimes \ket{0}^{{\otimes (T-t)}}$.
We write $F(\rho_1, \rho_2)=\left(\tr\sqrt{\sqrt{\rho_1}\rho_2\sqrt{\rho_1}}\right)^2$ for the fidelity between $\rho_1$ and $\rho_2$.

@@

@@

\begin{thm}
	\label{thm:projection}
	Let $H_1, H_2$ be local Hamiltonians where $H_2\geq0$. Let $K=\ker H_2$ and
	$$J=\frac{10\norm{H_1}^2}{\lambda\left(H_2\big|_{K^\bot}\right)}$$
	then we have
	$$\lambda(H_1+JH_2)\geq\lambda\left(H_1\big|_K\right)-\frac{1}{8}$$
\end{thm}

### 2020-03-29 qpip.tex
Relate V_Ham p_acc with fidelity to ground state

\def\GS{\mathsf{Ham}}
\nc{\cVGS}{\ensuremath{\cV_\GS}}

\def\Samp{\mathsf{Samp}}
\nc{\PiSamp}{\ensuremath{\Pi_\Samp}}
\nc{\VSamp}{\ensuremath{V_\Samp}}
\nc{\PSamp}{\ensuremath{P_\Samp}}
\nc{\PSampstar}{\ensuremath{P_\Samp^*}}
\nc{\cVSamp}[1]{\ensuremath{\cV_{\Samp,#1}}}
\nc{\cPSamp}[1]{\ensuremath{\cP_{\Samp,#1}}}

@@

	Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction}, and
	$\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.

@@

	\begin{enumerate}
		\item The honest prover prepares $M=\varepsilon^{-8}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\varepsilon^{-3}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\varepsilon m$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	Now, for the other case, $j\notin J$, we have
	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr\left(H_{C'(x)}\rho_j}\right)<\varepsilon.$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}
	$$D(\rho_j, \ket{\phi_{C'(x)}})<\poly(\varepsilon)$$

>>>>

@@

	Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
	Let $\ket{\psi_{C'(x)}}$ be the local Hamiltonian ground state associated with $C'$ as defined in \Cref{thm:LHReduction},
	and $\cVGS$ be the way to check this ground state as defined in \Cref{AlgGroundStateCheck}.
	Recall that by \Cref{thm:HamCheck} there exists some $c\in\bbN$
	\Ethan{Maybe figure out the exact value of $c$ later? It's really messy due to multiple uses of projection lemma among other things}
	so that if $\cVGS$ accepts $\rho$ with probability at least $\frac{1}{2}-\kappa$ where $\kappa=\frac{\varepsilon}{(T+\frac{T}{\varepsilon})^c}$ then $F(\rho, \ket{\psi_{C'(x)}})\geq1-\varepsilon^2$
	\Ethan{TODO: That theorem currently doesn't even say that. At least write a corollary for it.}

@@

	\begin{enumerate}
		\item The honest prover prepares $M=\kappa^{-4}\varepsilon^{-4}\ln(\frac{T}{\varepsilon})$ copies \Ethan{That isn't an integer...?} of $\ket{\psi_{C'(x)}}$ and sends all of it to the verifier qubit-by-qubit.
		\item The verifier privately samples $I\subset[M]$ s.t. $\abs{I}=m$ where $m=\kappa^{-2}\varepsilon^{-1}$, and $k\xleftarrow{\$}[M]\setminus I$.
			For $i$ from $1$ to $M$, it chooses what to do to the $i$-th copy, $\rho_i$, as follows:
		\begin{enumerate}
			\item If $i\in I$, run $z_i\leftarrow\cV_{\GS}(\rho_i)$.
			\item Else if $i=k$, measure the data register \Ethan{Revisit this name} of $\rho_i$ and save the outcome as $y$.
			\item Else, discard $\rho_i$.
		\end{enumerate}
			Let $Z=\sum_{i\in I} z_i$. If $Z>\frac{m}{2}-\varepsilon m$ then the verifier accepts and outputs $y$. Otherwise, it rejects.
	\end{enumerate}
\end{protocol}

@@

	Now, for the other case, $j\notin J$, we have
	$$\Prob{\cV_\GS(\rho_i)=acc}>\frac{1}{2}-2\varepsilon\Rightarrow\sqrt{\tr H_{C'(x)}\rho_j}<\varepsilon.$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain \Ethan{Need notation for fidelity}
	$$D(\rho_j, \ket{\phi_{C'(x)}})<\poly(\varepsilon)$$
